---
title: "Peaceful Ancient Greece?"
format: 
  revealjs:    # oder 'html' für Webseite
    self-contained: false
execute:
  echo: false
---



## Context 

<br>

- Daniela Hammer **Tugendhat**, a leading Viennese **art historian**, noted many combat scenes in **ancient Greek sculptures**, but wasn’t sure why.

- For me, the answer was quite clear: ancient Greece' **number 1 hit**, the **Iliad** is set during an **ancient World War**, and war was a common way to **resolve conflicts**. The old Greeks were likely at war most of the time.

## Method

- To prove my point, I **scraped** the Wikipedia page that lists all armed conflicts in ancient greece (using rvest in R)   [Link](https://de.wikipedia.org/wiki/Liste_von_Kriegen_und_Schlachten_in_der_Antike)  

- And then cleaned myself through the data until I could calculate the *mean years of peace* in Greek Antiquity 


## Average years of peace 

```{r}
library(tidyverse)
library(plotly)

load("C:/Users/Manuel/Desktop/mholz/Forschung/Freetime/data.RDa")

df1 %>% 
  ggplot(aes(x=diff, group=1)) + 
  geom_density(fill="skyblue",alpha=0.6) + 
  geom_vline(xintercept=mean(df1$diff), linetype="dashed", color="red") +
  geom_text(aes(x=mean(df1$diff) + 5.5, label="Mean=8.41", y=0.1 ), colour="red")+ 
  theme_minimal() + 
  theme(base_size=22) +
  labs(x="Years of peace between conflicts", y="Density") + 
  theme(strip.text.x = element_text(size = 22))

```


## All conflicts 750B.C. - 100B.C. 

Interaktiver Plot! Fahre mit Mauszeiger über die Punkte

```{r, fig.width=10, fig.height=6}
set.seed(123)  # für Reproduzierbarkeit
df2$y_jitter <- runif(nrow(df2), min = -0.2, max = 0.2)

df2$year <- -1*df2$numbers1

p <- ggplot(df2, aes(x = year, y = y_jitter, color=Schlachtname, text=Schlachtname)) + 
  geom_point(size = 6) + 
  theme_minimal(base_size=22) +
  scale_y_continuous(limits=c(-0.5, 0.5), breaks=c(-0.5,0,0.5)) + 
  scale_x_continuous(limits=c(-750, -50), breaks=c(seq(-750, -50, 100))) + 
  theme(legend.position="none", , 
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 

ggplotly(p, tooltip = "text")
```



